\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Reza Same'ei}

\section{About Me}
Yet another \textbf{Backend Developer} with about 8 yrs of experience in building software components, with an increasing interest on \textbf{Distributed Systems} and ​\textbf{Data Intensive} problems. I’m looking forward to gain more knowledge and experience on Big Data technologies and Distributed Systems design and implementation.\\

\personal
  [sameei.github.io]
  {Tehran, Iran}
  {+98 (912) 6662695}
  {reza.samee@gmail.com}
  {\href{https://github.com/sameei}{@ Github}}
  {\href{https://stackoverflow.com/users/998642/reza-sameei}{@ Stackoverflow}}
  {\href{http://linkedin.com/in/reza-sameei/}{@ LinkedIn}}
  {\href{https://join.skype.com/invite/nINGOAMPxZdX}{@ Skype}}

\section{Work experience}

\begin{eventlist}

\item{March 2019 -- Present}
  {TrialBlaze. \textbf{Remotely}; Perth, Australia}
  {Backend Developer}
  \\Build components to process non-standard ODM files and use \textbf{user defined logics}, expressed in a simple AST, to calculate entitlements and invoice, with a team of 4. Understaning the domain without adequate informtion and trying to design the system to maximum flexibilty was of our challenges.\\Toolbox : Java, Drools, Docker, Postgres, Google Cloud, Go.

\item{March 2016 -- Dec 2018}
  {Bisphone. Tehran, Iran}
  {Backend Developer}
  \\Lead a team of 2 to build and maintain more than 10 \textbf{data intensive} components, in different forms such as RPC services or \textbf{stream and batch} data processing jobs, to support main product: Bisphone, a messaging and voice-call application.\\Dealing with \textit{consistency} issues amid microservices and reaching better \textit{high availability} rate were our main challenges while we were responsible to analyse and design for requested features from bussines team.\\Toolbox : Scala, Akka, Flink, Cassandra, Kafka, MySQL, ELK.

\item{Oct 2014 -- Nov 2015}
  {ImenPardis. Tehran, Iran}
  {Backend Developer}
  \\Implement backend services to support main product : frist version of Bisphone. I also deployed ELK to use it as our monitoring platform at that time.\\Toolbox: Scala, Akka/Spary, MySQL, ELK, RabbitMQ, XMPP.

\item{July 2013 -- Sep 2014}
  {Armaghan Rahe Talaie. Tehran, Iran}
  {Web Developer}
  \\Analyse requirement and Build a new Web based SMS Panel for company.\\Toolbox: PHP, Doctrine ORM, MySQL, RabbitMQ, and JavaScript.

\item{Sep 2011 -- July 2013}
  {Shiveh Co. Tehran, Iran}
  {Junior Web Developer}
  \\Started as a Junior, I was responsible to develop web based GIS application. But very soon I introduced Zend Framework, Propel ORM, CanJs (a javascript MVC framework), to the team, and I got more responsibility in team such as attending meetings with customers, and maintaining services (Linux).\\Toolbox: PHP, MySQL, JQuery, CanJS, Google Map API, SVN.

\end{eventlist}

\section{Education}

\begin{yearlist}

\item{2009-2011}
  {Associate Degree}
  {Software Engineering; Technical \& Vocational University, Karaj, Iran}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
  \item{English}{B1}
  \item{Persian}{Native}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Tools}
  {Scala, Akka, AkkaStream, Java, Reactor, Git, SQL, Cassandra, Kafka, Apache Flink, Docker, Google Cloud}

\item{Concepts}
  {Distributed Systems, Concurrency, Stream Processing,
  Functional Programming, OOP, DDD, Agility, JVM Performance}

\item{Hands on}
  {Spark, Hadoop, Cadence, Go, Kubernettes, Pulsar, Zookeeper}

\item{Interests}
  {Data Intensive Applications, Distributed System}

\end{factlist}

\end{document}
